fairmetrics: An R package for group fairness evaluation

### 2025-08-07 utils/joss_paper/paper.Rmd
dynamically renaming CI columns

$performance
                                    Metric Group1 Group2
1                 Positive Prediction Rate   0.17   0.08
2     Conditional Positive Prediction Rate   0.34   0.21
3                      False Negative Rate   0.38   0.62
4                      False Positive Rate   0.08   0.03
5            Avg. Predicted Positive Prob.   0.46   0.37
6            Avg. Predicted Negative Prob.   0.15   0.10
7                Positive Predictive Value   0.62   0.66
8                Negative Predictive Value   0.92   0.90
9                              Brier Score   0.09   0.08
10                                Accuracy   0.87   0.88
11 (False Negative)/(False Positive) Ratio   1.03   3.24

$fairness
                           Metric Difference        Diff_CI Ratio     Ratio_CI
1              Statistical Parity       0.09   [0.05, 0.13]  2.12 [1.48, 3.05]
2  Conditional Statistical Parity       0.13   [0.05, 0.21]  1.62 [1.17, 2.24]
3               Equal Opportunity      -0.24 [-0.39, -0.09]  0.61 [0.44, 0.86]
4             Predictive Equality       0.05   [0.02, 0.08]  2.67 [1.38, 5.15]
5      Balance for Positive Class       0.09   [0.04, 0.14]  1.24 [1.09, 1.42]
6      Balance for Negative Class       0.05   [0.03, 0.07]  1.50 [1.29, 1.75]
7      Positive Predictive Parity      -0.04  [-0.21, 0.13]  0.94 [0.71, 1.24]
8      Negative Predictive Parity       0.02  [-0.02, 0.06]  1.02 [0.98, 1.07]
9              Brier Score Parity       0.01  [-0.01, 0.03]  1.12 [0.89, 1.43]
10        Overall Accuracy Parity      -0.01  [-0.05, 0.03]  0.99 [0.94, 1.04]
11             Treatment Equality      -2.21  [-4.44, 0.02]  0.32  [0.14, 0.7]
```

>>>>

$performance
                                    Metric GroupFemale GroupMale
1                 Positive Prediction Rate        0.17      0.08
2     Conditional Positive Prediction Rate        0.34      0.21
3                      False Negative Rate        0.38      0.62
4                      False Positive Rate        0.08      0.03
5            Avg. Predicted Positive Prob.        0.46      0.37
6            Avg. Predicted Negative Prob.        0.15      0.10
7                Positive Predictive Value        0.62      0.66
8                Negative Predictive Value        0.92      0.90
9                              Brier Score        0.09      0.08
10                                Accuracy        0.87      0.88
11 (False Negative)/(False Positive) Ratio        1.03      3.24

$fairness
                           Metric Difference    95% Diff CI Ratio 95% Ratio CI
1              Statistical Parity       0.09   [0.05, 0.13]  2.12 [1.48, 3.05]
2  Conditional Statistical Parity       0.13   [0.05, 0.21]  1.62 [1.17, 2.24]
3               Equal Opportunity      -0.24 [-0.39, -0.09]  0.61 [0.44, 0.86]
4             Predictive Equality       0.05   [0.02, 0.08]  2.67 [1.38, 5.15]
5      Balance for Positive Class       0.09   [0.04, 0.14]  1.24 [1.09, 1.42]
6      Balance for Negative Class       0.05   [0.03, 0.07]  1.50 [1.29, 1.75]
7      Positive Predictive Parity      -0.04  [-0.21, 0.13]  0.94 [0.71, 1.24]
8      Negative Predictive Parity       0.02  [-0.02, 0.06]  1.02 [0.98, 1.07]
9              Brier Score Parity       0.01  [-0.01, 0.03]  1.12 [0.89, 1.43]
10        Overall Accuracy Parity      -0.01  [-0.05, 0.03]  0.99 [0.94, 1.04]
11             Treatment Equality      -2.21  [-4.44, 0.02]  0.32  [0.14, 0.7]
```
